---
title: "Jennifer Deaton Assignment 12"
output: html_notebook
---

#### 1). Create an object named “marriage” that only contains data from 2014 for participants who are married or who were once married. Be sure to drop unused factor levels.
```{r}
library(tidyverse)
data <- gss_cat
View(data)
levels(data$marital)
data$marital <- as.character.factor(data$marital)
marriage <- data %>%
  filter(year == 2014, marital != "Never married", marital != "No answer")
marriage
```

#### 2). Provide a frequency table for the marriage data, sorted in descending order of frequency.
```{r}
library(dplyr)
freq.marriage <- marriage %>% 
  count(marital) %>% 
  arrange(desc(n))
freq.marriage
```
#### 3). Create a bar graph to illustrate the frequency distribution. Put the bars in ascending order, from left to right.
```{r}
marriage$marital <- fct_infreq(marriage$marital)
marriage$marital <- fct_rev(marriage$marital)

ggplot(marriage, aes(x = marital)) +
  geom_bar() 
```

#### 4). Calculate the mean age for each level in the marriage data.
```{r}
marriage %>%
  group_by(marital) %>%
  summarize(age = mean(age, na.rm = TRUE))
```
#### 5). Construct a graph that shows income by age for each marital status category. On your graph, combine all non-income categories into one category called “Other.” Put this category at one end of the income axis on your graph. (10 points)
```{r}
levels(marriage$rincome)
marriage %>% 
  mutate(rincome = fct_collapse(rincome,
                                Other = c("No answer", "Don't know", "Refused", 
                                          "Not applicable"))) %>%
  ggplot(aes(x = age, y = rincome, group = marital)) +
  facet_wrap(vars(marital)) +
  geom_point(aes(color = marital)) +
  geom_jitter(aes(color = marital)) + 
  labs(title = "Income by Age for Each Marital Category")

```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

